A survey of generic IND-CCA2 transformations

### 2024-07-05 faster-fo-transform/cca-transform-survey/main.tex
described gamma-spread and rigidity

>>>>

\subsubsection{Spread and rigidity}
The spread of a public key encryption scheme measures the diffusion the encryption routine's output. The higher the spread, the lower the probability of obtaining any specific ciphertext.

\begin{definition}[$\gamma$-spread]\label{def:gamma-spread}
    For a given keypair $(\pk, \sk)$ and plaintext message $m \in \mathcal{M}$, the \emph{min-entropy} of the encryption routine is:

    $$\operatorname{min-entropy}(\pk, m) := -\log_2\left( 
        \max_{c \in \mathcal{C}} P\left\lbrack
            c = \encrypt(\pk, m)
        \right\rbrack
    \right) $$

    A $\pke$ has $\gamma$-spread if for all keypairs $(\pk, \sk)$ and plaintext $m \in \mathcal{M}$:

    $$
        \operatorname{min-entropy}(\pk, m) \leq \gamma
    $$
\end{definition}

Having $\gamma$ sperad means that for any keypair $(\pk, \sk)$, plaintext $m$, and ciphertext $c$:

$$
P\left\lbrack c = \encrypt(\pk, m) \right\rbrack \leq 2^{-\lambda}
$$

Finally, \emph{rigidity} conveys the idea that a ciphertext cannot be perturbed without becoming either invalid or decrypting to another plaintext

\begin{definition}[rigidity]\label{def:rigidity}
    $\pke(\keygen, \encrypt, \decrypt)$ is \emph{rigid} if for all keypairs $(\pk, \sk)$ and ciphertext $c$, either $\decrypt(\sk, c) = \bot$ or $\encrypt\left(\pk, \decrypt(\sk, c)\right) = c$
\end{definition}
